Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-05-08 analysis/paper/paper.Rmd
add "RCBD" to statement about design
Correct paper so that it properly builds

The plot design was a split-plot design with four replicates where irrigation was the main plot and N rate was the split-plot.

@@

par(mfcol = c(3, 2))

@@

plot_estimates_paper(models[[3]])
mtext(text = "Leaf Severity", side = 2, line = 6)
mtext(text = "e", side = 3, line = 0, adj = 1, cex = 0.75)

plot_estimates_paper(models[[4]], main_title = "2016")
mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)

plot_estimates_paper(models[[5]])
mtext(text = "d", side = 3, line = 0, adj = 1, cex = 0.75)

plot_estimates_paper(models[[6]])
mtext(text = "f", side = 3, line = 0, adj = 1, cex = 0.75)

>>>>

The plot design was a split-plot randomised complete block design with four replicates where irrigation was the main plot and N rate was the split-plot.

@@

par(mfcol = c(2, 2))

@@

plot_estimates_paper(models[[3]], main_title = "2016")
mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)

plot_estimates_paper(models[[4]])
mtext(text = "d", side = 3, line = 0, adj = 1, cex = 0.75)
